\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadTwo}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubhead}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\normalsize#3}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\link}[2]{{\color{blue}\href{#1}{#2}}}

% \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%              CV STARTS HERE              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Nguyen Thanh Trung} & Email: \href{mailto:ngthanhtrung23@gmail.com}{ngthanhtrung23@gmail.com}\\
  & Mobile: +65 9850 0401
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubhead
      {Google}{Sep. 2016 -- Present}
      {Software Engineer}
      \resumeItemListStart
        \resumeItem{Working on Tez -- mobile payment application targeted at Indian users.}
        \resumeItem{Developing administration dashboards which combine and translate data from various backends into meaningful data points for Tez customer support, risk and compliance operators.}
        \resumeItem{Developing streaming batch jobs for processing over 3,000 log events per second and collect relevant data into Bigtable.}
        \resumeItem{Problem setting and co-ordinating problem setters' discussion for \link{https://code.google.com/codejam/kickstart/}{Google Codejam Kickstart}.}
        \resumeItem{Language/Technology: \textbf{Java}, \textbf{Go}, \textbf{protobuf}, \textbf{Spanner}, \textbf{Bigtable}, \textbf{Flume}.}
      \resumeItemListEnd

    \resumeSubhead
      {Garena}{Nov. 2015 -- Sep. 2016}
      {Software Engineer}
      \resumeItemListStart
        \resumeItem{Implemented payment and logistic system for Shopee ‐- mobile application for online shopping.}
        \resumeItem{Managed task queues for syncing 300,000 daily shipments' status with third-party logistics partners in Vietnam and Thailand.}
        \resumeItem{Language/Technology: \textbf{Python}, \textbf{Django}, \textbf{Javascript}.}
      \resumeItemListEnd

    \resumeSubhead
      {PayPal}{Jun. 2014 -- Nov. 2015}
      {Software Engineer}
      \resumeItemListStart
        \resumeItem{Implemented partner onboarding flow -- allow users to create PayPal accounts on various partner applications.}
        \resumeItem{Language/Technology: \textbf{Java}, \textbf{Node.js}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS----------
\section{Achievements \& Awards}
  \resumeSubHeadingListStart
    \resumeSubheadTwo
      {Ranked 15th in Facebook Hackercup}{2016}
      \resumeItemListStart
        \resumeItem{Competed individually to solve algorithmic problems in 2‐-3 hours. The contest is
          organized annually by Facebook with around \textbf{10,000} competitors. Ranked 15th in
          World Final round.}
      \resumeItemListEnd
    
    \resumeSubheadTwo
      {Ranked 15th in ACM ICPC World Final}{2016}
      \resumeItemListStart
        \resumeItem{Competed in a team of three to solve 10‐-12 algorithmic problems in five hours
          contest using C++ / Java.}
        \resumeItem{Highest place amongst all Vietnamese teams participated in ACM ICPC.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {ACM ICPC Regional Champion}{2015}
      \resumeItemListStart
        \resumeItem{Champion of Jakarta ACM ICPC Regional 2015 and 3rd place in Singapore ACM ICPC Regional 2015.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Top 150 in Google Code Jam}{2013, 2014, 2015}
      \resumeItemListStart
        \resumeItem{Competed individually to solve 4 algorithmic problems in 2.5 hours. The contest is
        organized annually by Google with over 10,000 competitors. Placed 93rd in 2013, 126th in 2014
        and 121st in 2015.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Ranked 17th in ACM ICPC World Final}{2012}
  \resumeSubHeadingListEnd


%----------ACTIVITIES------------
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubheadTwo
      {Administrator, Contest Manager at \link{http://vnoi.info}{vnoi.info}}{Jun. 2010 -- Present}
      \resumeItemListStart
        \resumeItem{Leading a team of 5--10 people in creating problemsets, managing contest platform and
          raising funds for yearly programming competitions with over 250 participants.}
        \resumeItem{Managing \link{https://www.facebook.com/groups/VNOIForum/}{VNOI Facebook group} for algorithmic discussions with 8,000 members.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Coach for National Olympiad team}{Jun. 2010 -- Aug. 2013}
      \resumeItemListStart
        \resumeItem{Taught programming and algorithms to a group of 20 high school students preparing
          for Vietnamese National Olympiads in Informatics.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubhead
      {Nanyang Technological University}{Aug. 2010 -- May. 2014}
      {Bachelor of Computer Science;  GPA: 4.84/5.0}
  \resumeSubHeadingListEnd

\end{document}
