\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadTwo}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubhead}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\normalsize#3}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\link}[2]{{\color{blue}\href{#1}{#2}}}

% \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%              CV STARTS HERE              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Pham Van Hanh} & Email: \href{mailto:vanhanh.pham@gmail.com}{vanhanh.pham@gmail.com}\\
  & Mobile: +84 70 50 60 162
\end{tabular*}


%----------SUMMARY-----------------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItemListStart
      \resumeItem{Software Engineer Intern at Google in 2019, Facebook in 2017 \& 2018}
      \resumeItem{IOI 2015 gold medalist, ICPC World Finals 2016, 2017 \& 2019}
      \resumeItem{Experience with C++, Java, JavaScript, PHP, OCaml, HTML, Hack \& React}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubhead
      {Google}{Jul. 2019 -- Oct. 2019}
      {Software Engineer Intern}
      \resumeItemListStart
      	\resumeItem{Implemented data pipeline for sending notifications to channel creators in YouTube.}
	\resumeItem{Language/Technology: \textbf{C++} \& \textbf{Database}.}
      \resumeItemListEnd

    \resumeSubhead
      {Facebook}{Jun. 2018 -- Sep. 2018}
      {Software Engineer Intern}
      \resumeItemListStart
        \resumeItem{Implemented a source-to-source compiler to convert JavaScript code of new versions to older versions.}
        \resumeItem{Language/Technology: \textbf{Abstract syntax tree}, \textbf{JavaScript} \& \textbf{OCaml}.}
      \resumeItemListEnd

    \resumeSubhead
      {Facebook}{Jun. 2017 -- Sep. 2017}
      {Software Engineer Intern}
      \resumeItemListStart
        \resumeItem{Implemented features and user interface on WWW and mobile for group task management in Workplace.}
        \resumeItem{Language/Technology: \textbf{Hack (PHP)}, \textbf{React (JavaScript)}, \textbf {HTML} \& \textbf{CSS}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS----------
\section{Achievements and Awards}
  \resumeSubHeadingListStart
    \resumeSubheadTwo
      {Vietnam Golden Globe Award}{2018}
      \resumeItemListStart
        \resumeItem{An annual award granted by Ministry of Science and Technology for 10 best young talents in technology.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {International Collegiate Programming Contest (ICPC) -- World Finals}{2016, 2017, 2019}
      \resumeItemListStart
        \resumeItem{Competed in a team of three to solve 10‐-13 algorithmic problems in 5 hours using C++ \& Java.}
        \resumeItem{About 50,000 students from 3,000 universities took part each year.}
	\resumeItem{Ranked \textbf{28th} in 2016, \textbf{34th} in 2017 (as contestant) \& honorable mention in 2019 (as co-coach).}
      \resumeItemListEnd

    \resumeSubheadTwo
      {ICPC Regional Contests}{2015, 2016}
      \resumeItemListStart
        \resumeItem{\textbf{Champion} of 2015 ICPC Hanoi Regional \& second place in the 2016 ICPC Nha Trang Regional.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Champion of National Informatics Olympiad for University students}{2016, 2017}
      \resumeItemListStart
        \resumeItem{Competed individually to solve 4 algorithmic problems in 3 hours using C++ \& Java.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {First prize in National Mathematics Olympiad for University students}{2016, 2017}
      \resumeItemListStart
        \resumeItem{Competed individually to solve problems about linear algebra in 3 hours.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Gold medalist at International Olympiad in Informatics for High school students}{2015}
      \resumeItemListStart
        \resumeItem{Competed individually in 2 days to solve 3 algorithmic problems in 5 hours on each day.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%----------ACTIVITIES------------
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubheadTwo
      {Member of Judging Committee for ICPC}{Oct. 2017 -- Present}
      \resumeItemListStart
        \resumeItem{Created algorithmic problems, implemented solutions and prepared testing datasets for ICPC national and regional contests hosted in Vietnam.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Teacher of Vietnamese IOI team}{Jun. 2016 -- Present}
      \resumeItemListStart
        \resumeItem{Teaching advanced programming techniques and competing strategies for all Vietnamese contestants in International Olympiad in Informatics.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubhead
      {University of Engineering and Technology - Vietnam National University}{Sep. 2015 -- Jan. 2020}
      {Student of Computer Science;  GPA: 3.58/4.00 (4th year)}

  \resumeSubHeadingListEnd

\end{document}
